---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7")

library(pacman)


p_load(dplyr, lmerTest, ggplot2, stringr, plyr, caret, modelr, tidyverse, MASS, simr, MuMIn, cvTools, hydroGOF, lsr, pastecs, crqa, dostats, readr, stats, pROC, groupdata2, knitr, gridExtra)

file1 = read.csv("Study1_G1_T1_Synchronous.csv")

```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment


### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?


```{r setup, include=FALSE}


rplot1 = ggplot(file1, aes(time, Resp1)) + geom_line()
rplot1
rplot2 = ggplot(file1, aes(time, Resp2)) + geom_line()
rplot2

resp_plot = grid.arrange(rplot1, rplot2, ncol = 2)

#downsampling
d1 = file1%>% 
  group(n= 100, method= 'greedy') %>%       
  dplyr::summarise(time= mean(time,na.rm=T),HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T),Resp1 = mean(Resp1,na.rm=T),Resp2 = mean(Resp2,na.rm=T))


#outliers removal
removeOuts = function(ts,threshold){
  ts[ts> (mean(ts, na.rm=T)+
      (threshold*sd(ts,na.rm=T))) |
    ts < (mean(ts,na.rm=T) -
     (threshold*sd(ts,na.rm=T)))] = 
mean(ts, na.rm=T)
return(ts)}

threshold=2.5
d$HR1 = removeOuts(d$HR1,threshold)

#scaling signals
d1$Resp1S=scale(d1$Resp1)  
d1$Resp2S=scale(d1$Resp2)  
d1$HR1S=scale(d1$HR1) 
d1$HR2S=scale(d1$HR2)


#plotting 

rplot1.1 = ggplot(d1, aes(time, Resp1)) + geom_line()
rplot1.1
rplot2.1 = ggplot(d1, aes(time, Resp2)) + geom_line()
rplot2.1

resp_plot = grid.arrange(rplot1.1, rplot2.1, ncol = 2)

#Plotting respiration

col_resp_plot = ggplot(d1, aes(time, Resp1)) + geom_line ()+ 
  geom_line(aes(time, Resp2), color = "blue")

col_resp_plot

hplot1.1 = ggplot(d1, aes(time, HR1)) + geom_line()
hplot1.1
hplot2.1 = ggplot(d1, aes(time, HR2)) + geom_line()
hplot2.1

#Plotting heart rate

col_HR_plot = ggplot(d1, aes(time, HR1)) + geom_line ()+ 
  geom_line(aes(time, HR2), color = "red")

col_HR_plot


# - Can you eye-ball which condition if any displays more physiological coordination?





#Running CRQA on respiration

#Finding the optimal parameters: run on all pairs:

#list you ned for optimizeparam function
par = list(lgM =  20, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

#get parameters for rqa
ans = optimizeParam(d1$Resp1, d1$Resp2, par, min.rec = 3.5, max.rec = 4.5)
ans

#try() --> selvom den ikke får en værdi så looper den videre/crasher ikke

#Choose a common value for delay, emb.dim and radius
#File has to be imported twise since crqa plot compares two timeseries
Results=crqa (d1$Resp1, d1$Resp2, delay=26, embed=7, radius=25.47183,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#Represent the plot:
RP=Results$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP)) 
cols = c("white","blue4")
image(RP, xlab = "", ylab = "", col = cols)

#Save variables from results to seperate variables

RR = Results$RR
DET = Results$DET
MAXL = Results$maxL #maximal trajectory
L = Results$L #mean trajectory
ENTR = Results$ENTR
LAM = Results$LAM
TT = Results$TT


#bind
rqa = data.frame(RR, DET, MAXL, L, ENTR, LAM, TT)



# RUNNING RQA ON HR

#list you ned for optimizeparam function
par = list(lgM =  20, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

#get parameters for rqa
ans = optimizeParam(d1$HR1, d1$HR2, par, min.rec = 3.5, max.rec = 4.5)
ans

#try() --> selvom den ikke får en værdi så looper den videre/crasher ikke

#Choose a common value for delay, emb.dim and radius
#File has to be imported twise since crqa plot compares two timeseries
Results=crqa (d1$HR1, d1$HR2, delay=26, embed=7, radius=25.47183,normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#Represent the plot:
RP=Results$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP)) 
cols = c("white","blue4")
image(RP, xlab = "", ylab = "", col = cols)

#Save variables from results to seperate variables

RR = Results$RR
DET = Results$DET
MAXL = Results$maxL #maximal trajectory
L = Results$L #mean trajectory
ENTR = Results$ENTR
LAM = Results$LAM
TT = Results$TT

#bind
rqa = data.frame(RR, DET, MAXL, L, ENTR, LAM, TT)



# - Does this (RQA) tell you more than just eyeballing the plots?

```



```{r}

#Some functions


#downsampling
downsample = function(x){
  x%>% 
  group(n= 100, method= 'greedy') %>%       
  dplyr::summarise(time= mean(time,na.rm=T),HR1 = mean(HR1,na.rm=T),HR2 = mean(HR2,na.rm=T),Resp1 = mean(Resp1,na.rm=T),Resp2 = mean(Resp2,na.rm=T))
return(x)}


#outliers removal
removeOuts = function(ts,threshold){
  ts[ts> (mean(ts, na.rm=T)+
      (threshold*sd(ts,na.rm=T))) |
    ts < (mean(ts,na.rm=T) -
     (threshold*sd(ts,na.rm=T)))] = 
mean(ts, na.rm=T)
return(ts)}
threshold=2.5
d$HR1 = removeOuts(d$HR1,threshold)

#scaling signals
scale = function(x){
x$Resp1S=scale(x$Resp1)  
x$Resp2S=scale(x$Resp2)  
x$HR1S=scale(x$HR1) 
x$HR2S=scale(x$HR2)
}


#rqa function
rqa_func = function(x, y){
  
  par = list(lgM =  20, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2, minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")
  
  
  param = try(optimizeParam(x, y, par, min.rec = 3.5, max.rec = 4.5))
  
  if (length(param)>1){
    Results = crqa(x, y, delay = param$delay, embed = param$emddim, radius = param$radius, normalize = 0, rescale = 0, mindiagline = 2, minvertline = 2)
  }else {
    Results = NULL
    param = NULL
    param$delay = NA
    param$emddim = NA
    param$radius = NA
    Results$RR = NA
    Results$DET = NA
    Results$maxL = NA
    Results$L = NA
    Results$ENTR = NA
    Results$LAM = NA
    Results$TT = NA
  }
  
  
  df = data.frame(delay = param$delay, embed = param$emddim, radius = param$radius, RR= Results$RR, DET = Results$DET, LMAX = Results$maxL, L = Results$L, ENTR = Results$ENTR, LAM = Results$LAM, TT = Results$TT)
  
  return(df)
  
}




```



### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

all_files = list.files(path = "CleanData", full.names = TRUE)


n = 1

#l?ser, scale, downsample, removeout, plot over resp og hr for partc 1 og 2

path = ("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData")

folder = file.path(path)



#Study1_G1_T1_Synchronous



setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData")
all_list = list.files(pattern= ".csv", recursive = TRUE)

for (i in all_list){
  
  
  x = read.csv(i, header = T)
  
  
  
  #downsample
  x1 = x%>% 
  group(n= 100, method= 'greedy') %>%       
  dplyr::summarise(
    time= mean(time,na.rm=T),
    HR1 = mean(HR1,na.rm=T),
    HR2 = mean(HR2,na.rm=T),
    Resp1 = mean(Resp1,na.rm=T),
    Resp2 = mean(Resp2,na.rm=T)
  )
  
  #remove outliers
  x1$Resp1 = removeOuts(x1$Resp1, threshold)
  x1$Resp2 = removeOuts(x1$Resp2, threshold)
  x1$HR1 = removeOuts(x1$HR1, threshold)
  x1$HR2 = removeOuts(x1$HR2, threshold)
  
  
  #scaling
  x1$Resp1S=scale(x1$Resp1)  
  x1$Resp2S=scale(x1$Resp2)  
  x1$HR1S=scale(x1$HR1) 
  x1$HR2S=scale(x1$HR2)
  

  
  # write file
  
  namefile = paste("Preprocess_", i)
  
  write_csv(x1, file.path("Preprocess",namefile))
  
  # print(n)
  # n = n+1
  

  }


setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData/Preprocess")
all_list_plot = list.files(pattern= ".csv", recursive = TRUE)
#n = 1

for (i in all_list_plot){
  
  
  x = read.csv(i, header = T)
  
  #plotting
  
  HRpS = ggplot(x, aes(time, HR1S)) + geom_line() + geom_line(aes(time, HR2S), color = "red")
  HRp = ggplot(x, aes(time, HR1)) + geom_line() + geom_line(aes(time, HR2), color = "red")
  RpS = ggplot(x, aes(time, Resp1S)) + geom_line() + geom_line(aes(time, Resp2S), color = "blue")
  Rp = ggplot(x, aes(time, Resp1)) + geom_line() + geom_line(aes(time, Resp2), color = "blue")

  
  #plot them together 
  plot_all = grid.arrange(HRpS, HRp, RpS, Rp)

  # Save plots so you can see them
  png(filename=paste0("plot_all", i,".png"))
  plot(plot_all)
  dev.off()
  
  
}

#List the ones that should be excluded


#Run CRQA

HR_Delay = NULL
HR_Embed = NULL
HR_Radius = NULL
Resp_Delay = NULL
Resp_Embed = NULL
Resp_Radius = NULL
study = NULL
group = NULL
trial = NULL
condition = NULL
n = n + 1
df = NULL

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData/Preprocess")
prep_list = list.files(pattern= ".csv", recursive = TRUE)


#Define input to parameter optimization
par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

#Optimize for each file
for (i in prep_list){
  
  x = read.csv(i, header = T)
  
  study = str_extract(x, "Study+\\d+") %>%   
      str_extract("\\d+")
  group = str_extract(x, "G+\\d+") %>%   
      str_extract("\\d+")
  trial = str_extract(x, "T+\\d+") %>%   
      str_extract("\\d+")
  condition = gsub(".*[_]([^.]+)[.].*", "\\1", x)

  #Get optimized parameters
  HR_ans = try(optimizeParam(x$HR1, x$HR2, par, min.rec= 2, max.rec= 8))
  Resp_ans = try(optimizeParam(x$Resp1, x$Resp2, par, min.rec= 2, max.rec= 8))
  
  #Save optimal parameters
  if (length(HR_ans) < 2){
    HR_Delay[n] = NA
    HR_Embed[n] = NA
    HR_Radius[n] = NA
  } else {
    HR_Delay[n] = HR_ans$delay
    HR_Embed[n] = HR_ans$emddim
    HR_Radius[n] = HR_ans$radius}
  
  #Save optimal parameters
  if (length(Resp_ans) < 2){
    Resp_Delay[n] = NA
    Resp_Embed[n] = NA
    Resp_Radius[n] = NA
  } else {
    Resp_Delay[n] = Resp_ans$delay
    Resp_Embed[n] = Resp_ans$emddim
    Resp_Radius[n] = Resp_ans$radius}
  
  #loop end
  print (n)
  n = n+1 
  }

HR_Delay = median(HR_Delay, na.rm=T)
HR_Delay

HR_DELAY = 20



HR_Embed = median(HR_Embed, na.rm = T)
HR_Embed

HR_EMBED = 1

#as suggested, add 1.2
HR_Radius = median(HR_Radius, na.rm = T)+1.2
HR_Radius

HR_RADIUS = 8.793347


Resp_Delay = median(Resp_Delay, na.rm = T)
Resp_Delay

Resp_DELAY = 26

Resp_Embed = median(Resp_Embed, na.rm = T)
Resp_Embed

Resp_EMBED = 2

Resp_Radius = median(Resp_Radius, na.rm = T)+1.2
Resp_Radius

Resp_RADIUS = 2.647569




# Finding the crqa results

# Loop real pairs
setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData/Preprocess")
clean_list_2 = list.files(pattern= ".csv", recursive =TRUE)


#Create lists for results
Study_l = NULL
Group_l = NULL
Trial_l = NULL
Condition_l = NULL

#CQRA
HR_RR = NULL
HR_DET = NULL
HR_NRLINE = NULL
HR_maxL = NULL
HR_L = NULL
HR_ENTR = NULL
HR_LAM = NULL
HR_TT = NULL
Resp_RR = NULL
Resp_DET = NULL
Resp_NRLINE = NULL
Resp_maxL = NULL
Resp_L = NULL
Resp_ENTR = NULL
Resp_LAM = NULL
Resp_TT = NULL
#iteration counter
n = 1


for (i in clean_list_2){
  ###Read file
  #Put the path together with the filename
  x = read.csv(i)
  
  #Extract demographics from filename
  Study_l [n] = str_extract(i, "Study+\\d+") %>%   
        str_extract("\\d+")
  Group_l [n] = NA
    #str_extract(i, "G+\\d+") %>%   
        #str_extract("\\d+")
  Trial_l [n] = NA
    #str_extract(i, "T+\\d+") %>%   
        #str_extract("\\d+")
  Condition_l [n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  

  #Do CRQA analysis - on HR
    HR_crqa_t = try(crqa (x$HR1, x$HR2, delay=HR_DELAY, embed=HR_EMBED, radius=HR_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(HR_crqa_t) < 2 ){
    HR_RR[n] = NA
    HR_DET[n] = NA
    HR_NRLINE[n] = NA
    HR_maxL[n] = NA
    HR_L[n] = NA
    HR_ENTR[n] = NA
    HR_LAM[n] = NA
    HR_TT[n] = NA
  } else {
    HR_RR[n] = HR_crqa_t$RR
    HR_DET[n] = HR_crqa_t$DET
    HR_NRLINE[n] = HR_crqa_t$NRLINE
    HR_maxL[n] = HR_crqa_t$maxL
    HR_L[n] = HR_crqa_t$L
    HR_ENTR[n] = HR_crqa_t$ENTR
    HR_LAM[n] = HR_crqa_t$LAM
    HR_TT[n] = HR_crqa_t$TT}
    
      #Do CRQA analysis - on Respiration
    Resp_crqa_t = try(crqa (x$Resp1, x$Resp2, delay=Resp_DELAY, embed=Resp_EMBED, radius=Resp_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(Resp_crqa_t) < 2 ){
    Resp_RR[n] = NA
    Resp_DET[n] = NA
    Resp_NRLINE[n] = NA
    Resp_maxL[n] = NA
    Resp_L[n] = NA
    Resp_ENTR[n] = NA
    Resp_LAM[n] = NA
    Resp_TT[n] = NA
  } else {
    Resp_RR[n] = Resp_crqa_t$RR
    Resp_DET[n] = Resp_crqa_t$DET
    Resp_NRLINE[n] = Resp_crqa_t$NRLINE
    Resp_maxL[n] = Resp_crqa_t$maxL
    Resp_L[n] = Resp_crqa_t$L
    Resp_ENTR[n] = Resp_crqa_t$ENTR
    Resp_LAM[n] = Resp_crqa_t$LAM
    Resp_TT[n] = Resp_crqa_t$TT}
  
  #Loop end
  print(n)
  n = n+1
  
  }

#Combine the list to create dataset
d_out_real = data.frame(cbind (Study_l, Group_l, Trial_l, Condition_l, HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT))

d_out_real$typepairs = "real"


write.csv(d_out_real, file="Results_Real.csv")







```

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs

```{r setup, include=FALSE}


# Creating shuffled pairs

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData/Preprocess")
clean_list = list.files(pattern= ".csv", recursive = FALSE)

#loop
for (i in clean_list) {

  x = read.csv(i, header = T)
  
  #Datapoints order = randomized/shuffled
  x$HR1r = sample(x$HR1, length(x$HR1))
  x$HR1 = x$HR1r
  x$HR2r = sample(x$HR2, length(x$HR2))
  x$HR2 = x$HR2r
  x$Resp1r = sample(x$Resp1, length(x$Resp1))
  x$Resp1 = x$Resp1r
  x$Resp2r = sample(x$Resp2, length(x$Resp2))
  x$Resp2 = x$Resp2r
  
  #create new files
  filename = paste("Shuffled/", i, sep="")
  write.csv(x, file = filename)
}

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/CleanData/Preprocess/Shuffled")
clean_list_3 = list.files(pattern= ".csv", recursive = FALSE)


for (i in clean_list_3){
  ###Read file
  #Put the path together with the filename
  x = read.csv(i)
  
  #Extract demographics from filename
  Study_l [n] = str_extract(i, "Study+\\d+") %>%   
        str_extract("\\d+")
  Group_l [n] = NA
    #str_extract(i, "G+\\d+") %>%   
        #str_extract("\\d+")
  Trial_l [n] = NA
    #str_extract(i, "T+\\d+") %>%   
        #str_extract("\\d+")
  Condition_l [n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  

  #Do CRQA analysis - on HR
    HR_crqa_t = try(crqa (x$HR1, x$HR2, delay=HR_DELAY, embed=HR_EMBED, radius=HR_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(HR_crqa_t) < 2 ){
    HR_RR[n] = NA
    HR_DET[n] = NA
    HR_NRLINE[n] = NA
    HR_maxL[n] = NA
    HR_L[n] = NA
    HR_ENTR[n] = NA
    HR_LAM[n] = NA
    HR_TT[n] = NA
  } else {
    HR_RR[n] = HR_crqa_t$RR
    HR_DET[n] = HR_crqa_t$DET
    HR_NRLINE[n] = HR_crqa_t$NRLINE
    HR_maxL[n] = HR_crqa_t$maxL
    HR_L[n] = HR_crqa_t$L
    HR_ENTR[n] = HR_crqa_t$ENTR
    HR_LAM[n] = HR_crqa_t$LAM
    HR_TT[n] = HR_crqa_t$TT}
    
      #Do CRQA analysis - on Respiration
    Resp_crqa_t = try(crqa (x$Resp1, x$Resp2, delay=Resp_DELAY, embed=Resp_EMBED, radius=Resp_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(Resp_crqa_t) < 2 ){
    Resp_RR[n] = NA
    Resp_DET[n] = NA
    Resp_NRLINE[n] = NA
    Resp_maxL[n] = NA
    Resp_L[n] = NA
    Resp_ENTR[n] = NA
    Resp_LAM[n] = NA
    Resp_TT[n] = NA
  } else {
    Resp_RR[n] = Resp_crqa_t$RR
    Resp_DET[n] = Resp_crqa_t$DET
    Resp_NRLINE[n] = Resp_crqa_t$NRLINE
    Resp_maxL[n] = Resp_crqa_t$maxL
    Resp_L[n] = Resp_crqa_t$L
    Resp_ENTR[n] = Resp_crqa_t$ENTR
    Resp_LAM[n] = Resp_crqa_t$LAM
    Resp_TT[n] = Resp_crqa_t$TT}
  
  #Loop end
  print(n)
  n = n+1
  
  }

#Combine the list to create dataset
d_out_shuffled = data.frame(cbind (Study_l, Group_l, Trial_l, Condition_l, HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT))

d_out_shuffled$typepairs = "shuffled"


write.csv(d_out_shuffled, file="Results_Shuffled.csv")






```

 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


#Making surrogate pairs --> first looped through study 1, then 2

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/adm_7")

prepro_filelist = list.files(pattern = "Study2") # load the preprocessed files

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df_surro= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df_surro)=NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df_surro$V2)))) #create pairs, i.e. unique group numbers

SurrogateList = expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.



# Per each condition
for (co in c("Synchronous","TurnTaking")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study2_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study2_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2,Resp1S=d1$Resp1S,Resp2S=d2$Resp2S,HR1S=d1$HR1S,HR2S=d2$HR2S)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2,Resp1S=d2$Resp1S,Resp2S=d1$Resp2S,HR1S=d2$HR1S,HR2S=d1$HR2S)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1,Resp1S=d1$Resp1S,Resp2S=d2$Resp1S,HR1S=d1$HR1S,HR2S=d2$HR1S)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2,Resp1S=d2$Resp2S,Resp2S=d1$Resp2S,HR1S=d2$HR2S,HR2S=d1$HR2S)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}

#It only worked with the bad data --> so I deleted manually the surrogate pairs created by the bad data

n = 1

HR_Delay_surro = NULL
HR_Embed_surro = NULL
HR_Radius_surro = NULL
Resp_Delay_surro = NULL
Resp_Embed_surro = NULL
Resp_Radius_surro = NULL
study_surro = NULL
group_surro = NULL
trial_surro = NULL
condition_surro = NULL
n = n + 1
df = NULL

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/adm_7/surrogate")
surro_list = list.files(pattern= ".csv", recursive = TRUE)


#Define input to parameter optimization
par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

#Optimize for each file
for (i in surro_list){
  
  x = read.csv(i, header = T)
  
  study_surro = str_extract(x, "Study+\\d+") %>%   
      str_extract("\\d+")
  group_surro = str_extract(x, "G+\\d+") %>%   
      str_extract("\\d+")
  trial_surro = str_extract(x, "T+\\d+") %>%   
      str_extract("\\d+")
  condition_surro = gsub(".*[_]([^.]+)[.].*", "\\1", x)

  #Get optimized parameters
  HR_ans = try(optimizeParam(x$HR1, x$HR2, par, min.rec= 2, max.rec= 8))
  Resp_ans = try(optimizeParam(x$Resp1, x$Resp2, par, min.rec= 2, max.rec= 8))
  
  #Save optimal parameters
  if (length(HR_ans) < 2){
    HR_Delay_surro[n] = NA
    HR_Embed_surro[n] = NA
    HR_Radius_surro[n] = NA
  } else {
    HR_Delay_surro[n] = HR_ans$delay
    HR_Embed_surro[n] = HR_ans$emddim
    HR_Radius_surro[n] = HR_ans$radius}
  
  #Save optimal parameters
  if (length(Resp_ans) < 2){
    Resp_Delay_surro[n] = NA
    Resp_Embed_surro[n] = NA
    Resp_Radius_surro[n] = NA
  } else {
    Resp_Delay_surro[n] = Resp_ans$delay
    Resp_Embed_surro[n] = Resp_ans$emddim
    Resp_Radius_surro[n] = Resp_ans$radius}
  
  #loop end
  print (n)
  n = n+1 
  }


setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/adm_7/surrogate")
clean_list_3 = list.files(pattern= ".csv", recursive = FALSE)


for (i in clean_list_3){
  ###Read file
  #Put the path together with the filename
  x = read.csv(i)
  
  #Extract demographics from filename
  Study_l [n] = str_extract(i, "Study+\\d+") %>%   
        str_extract("\\d+")
  Group_l [n] = NA
    #str_extract(i, "G+\\d+") %>%   
        #str_extract("\\d+")
  Trial_l [n] = NA
    #str_extract(i, "T+\\d+") %>%   
        #str_extract("\\d+")
  Condition_l [n] = gsub(".*[_]([^.]+)[.].*", "\\1", i)
  

  #Do CRQA analysis - on HR
    HR_crqa_t = try(crqa (x$HR1, x$HR2, delay=HR_DELAY, embed=HR_EMBED, radius=HR_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(HR_crqa_t) < 2 ){
    HR_RR[n] = NA
    HR_DET[n] = NA
    HR_NRLINE[n] = NA
    HR_maxL[n] = NA
    HR_L[n] = NA
    HR_ENTR[n] = NA
    HR_LAM[n] = NA
    HR_TT[n] = NA
  } else {
    HR_RR[n] = HR_crqa_t$RR
    HR_DET[n] = HR_crqa_t$DET
    HR_NRLINE[n] = HR_crqa_t$NRLINE
    HR_maxL[n] = HR_crqa_t$maxL
    HR_L[n] = HR_crqa_t$L
    HR_ENTR[n] = HR_crqa_t$ENTR
    HR_LAM[n] = HR_crqa_t$LAM
    HR_TT[n] = HR_crqa_t$TT}
    
      #Do CRQA analysis - on Respiration
    Resp_crqa_t = try(crqa (x$Resp1, x$Resp2, delay=Resp_DELAY, embed=Resp_EMBED, radius=Resp_RADIUS, normalize=0, rescale=0, mindiagline = 2, minvertline = 2)) 
  
  if (length(Resp_crqa_t) < 2 ){
    Resp_RR[n] = NA
    Resp_DET[n] = NA
    Resp_NRLINE[n] = NA
    Resp_maxL[n] = NA
    Resp_L[n] = NA
    Resp_ENTR[n] = NA
    Resp_LAM[n] = NA
    Resp_TT[n] = NA
  } else {
    Resp_RR[n] = Resp_crqa_t$RR
    Resp_DET[n] = Resp_crqa_t$DET
    Resp_NRLINE[n] = Resp_crqa_t$NRLINE
    Resp_maxL[n] = Resp_crqa_t$maxL
    Resp_L[n] = Resp_crqa_t$L
    Resp_ENTR[n] = Resp_crqa_t$ENTR
    Resp_LAM[n] = Resp_crqa_t$LAM
    Resp_TT[n] = Resp_crqa_t$TT}
  
  #Loop end
  print(n)
  n = n+1
  
  }

#Combine the list to create dataset
d_out_surrogate = data.frame(cbind (Study_l, Group_l, Trial_l, Condition_l, HR_RR, HR_DET, HR_NRLINE, HR_maxL, HR_L, HR_ENTR, HR_LAM, HR_TT, Resp_RR, Resp_DET, Resp_NRLINE, Resp_maxL, Resp_L, Resp_ENTR, Resp_LAM, Resp_TT))

d_out_surrogate$typepairs = "surrogate"


write.csv(d_out_surrogate, file="Results_Surrogate.csv")

setwd("C:/Users/Bruger/Desktop/Programming/Semester 3/asm_7/adm_7/results")

Real = read.csv("Results_Real.csv", header = T)
Shuffled = read.csv("Results_Shuffled.csv", header = T)
Surrogate = read.csv("Results_Surrogate.csv", header = T)

sub1 = rbind(Real, Shuffled)
sub2 = rbind(sub1, Surrogate)


```


### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#kan pairs predicte RR for HR og Resp, random effect group

model_1 = lmer(HR_RR ~ typepairs + (1+Study_l|Condition_l), data = sub2, REML = F)
summary(model_1)

model_2 = lmer(Resp_RR ~ typepairs + (1+Study_l|Condition_l), data = sub2, REML = F)
summary(model_2)

model_3= lmer(HR_RR ~ Condition_l + (1+Study_l|typepairs), data = sub2, REML = F)
summary(model_3)

model_4= lmer(Resp_RR ~ Condition_l + (1+Study_l|typepairs), data = sub2, REML = F)
summary(model_4)


```


### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them
 
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```